---
title: "Regression - EDA"
author: "Group 35"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Preprocessing

```{r}
udemy <- read.csv("udemy.csv")
udemy <- udemy[udemy$num_subscribers!=0,]
```


```{r}
is.factor(udemy$is_paid)
is.factor(udemy$level)
is.factor(udemy$subject)
udemy$is_paid<-as.factor(udemy$is_paid)
is.factor(udemy$is_paid)

contrasts(udemy$is_paid)
contrasts(udemy$level)
contrasts(udemy$subject)
```

train-test split
```{r}
RNGkind(sample.kind = "Rejection")
set.seed(199)
samp<-sample.int(nrow(udemy), floor(.50*nrow(udemy)), replace = F)
train<-udemy[samp, ]
test<-udemy[-samp, ]
head(train)
```

# EDA

```{r pressure, echo=FALSE}

pairs(train[,c(5:8,10,13)], lower.panel = NULL, main="Scatterplot of Quantitative Variables")


## Numerical summaries
correlation<-round(cor(train[,c(5:8,10,13)]),3)
correlation


### Boxplots of categorical variables vs response variables
boxplot(num_subscribers~is_paid, main="Number of Subscribers by Is_Paid",data = train)
boxplot(num_subscribers~subject, main="Number of Subscribers by Subject",data = train)
boxplot(num_subscribers~level, main="Number of Subscribers by Level",data = train)
subscribers <- subset(num_subscribers,num_subscribers < 50000)

#not easy to see so subset the data
levels <- subset(level,num_subscribers < 50000)
boxplot(subscribers~levels, main="Number of Subscribers by Level (below 50K)",data = train)
```


# linear regression

##initial model based on EDA: 1 quantitative var + all categorical vars
```{r}
initial<-lm(num_subscribers~ num_reviews + is_paid +subject, train)
summary(initial)
par(mfrow=c(2,2))
plot(initial)

library(MASS)
boxcox(initial) #lambda = 0.2
```

##initial model with transformed y
```{r}
train$num_subscribers2 <- (train$num_subscribers)**(0.2)
initial2 <-lm(num_subscribers2~ num_reviews + is_paid+subject, train)
summary(initial2)
par(mfrow=c(2,2))
plot(initial2)
```


## Forward Selection

### add the rest of quantitative variables one by one

Partial F-test whether to any other quantitaive variables is significant: the price, num_lectures, and content duration, days since published
```{r}
model2 <-lm(num_subscribers2~num_reviews +is_paid+subject +price+num_lectures+days_published+content_duration, train)
anova(initial2,model2) 
```
We reject null; one of them is significant. 


T-test on days_published. Significant. we should include it.
```{r}
model3 <-lm(num_subscribers2~num_reviews +is_paid+subject+days_published, train)
summary(model3)
```

T-test on content duration. Significant. we should include it.
```{r}
model4 <-lm(num_subscribers2~num_reviews + is_paid+subject+days_published+content_duration, train)
summary(model4)
```

Test on num_lectures. Significant. We should include it.
```{r}
model5 <-lm(num_subscribers2~num_reviews +is_paid+subject+days_published+content_duration+num_lectures, train)
summary(model5)
```

Test on price. Significant. We should include it.
```{r}
model6 <-lm(num_subscribers2~num_reviews +is_paid+subject+days_published+content_duration+price, train)
summary(model6) # make 
```

Content duration became insignificant. remove it now.
```{r}
model6.2 <-lm(num_subscribers2~num_reviews +is_paid+subject+days_published+price, train)
summary(model6.2) 
```


### add the rest of categorical variables (just level)

```{r}
model7 <-lm(num_subscribers2~num_reviews+is_paid+subject+days_published+price+level, train)
summary(model7)
anova(model6, model7) #significant; use model7
```

final model for now:
```{r}
final <-lm(num_subscribers2~num_reviews +is_paid+subject+days_published+price+level, train)
summary(final)
```


## Backwards Elimination

```{r}
all <- lm(num_subscribers2 ~ num_reviews + price + num_lectures + content_duration +days_published + is_paid+subject+level, train)
summary(all)
```

1.remove content duration
```{r}
reduced1 <- lm(num_subscribers2 ~ num_reviews + price + num_lectures +days_published + is_paid+subject+level, train)
summary(reduced1)
```

2. remove num_lectures
```{r}
reduced2 <- lm(num_subscribers2 ~ num_reviews + price +days_published + is_paid+subject+level, train)

summary(reduced2)
plot(reduced2)
```
reduced2 is the same as final.


## model diagnostics
```{r}
par(mfrow=c(2,2))
plot(final)
```

Remove outliers:
```{r}
train2<-train[(rownames(train)!="3233" & rownames(train)!="3205" &  rownames(train)!="3248") ,]
final2 <-lm(num_subscribers2~num_reviews +is_paid+subject+days_published+price+level, train2)
summary(final2)
plot(final2) #the real real final...
```


# Comparasion (initial w/ tranformed y vs final)

1. R^2
```{r}
summary(initial2)$adj.r.squared #0.4133557
summary(final2)$adj.r.squared #0.5130349
```


2. train mse
```{r}
pred_train1 <- predict(initial2, newdata = train, type = 'response')
train.mse1 <-mean((pred_train1-train$num_subscribers2)^2) #1.467734

test$num_subscribers2 <-(test$num_subscribers)^0.2 
pred_train2 <- predict(final2, newdata = train, type = 'response')
train.mse2 <-mean((pred_train2-train$num_subscribers2)^2) #1.443532

```

3. test mse
```{r}
pred_test1 <- predict(initial2, newdata = test, type = 'response')
test.mse1 <- mean((pred_test1-test$num_subscribers2)^2) #1.534977

pred_test2 <- predict(final2, newdata = test, type = 'response')
test.mse2 <-mean((pred_test2 - test$num_subscribers2)^2) # 1.491749
```




